Viscous Transport in Eroding Porous Media

### 2019-06-27 docs/transport/erosion_transport.tex
do the result section in transport paper

{\color{red}
This case is 100 bodies in a Hagen-Poiseuille flow. The background
flow is 
\begin{align}
  \UU(\xx)=U \left[
  \begin{array}{c}
    1-y^2 \\ 0
  \end{array}
  \right]
\end{align}
with floating flow rate $U$ such that pressure drop is fixed from x = -2 to x = 2.
We record the vorticity of 
fluid in colormap during the bodies erosion in Fig.~\ref{fig:Eroding100vort} and 
measure the gap sizes between bodies in Fig.~\ref{fig:Eroding100gap} at four equispaced times.
Since the vorticity is equivalent to the shear stress and the erosion is faster in the regions where
the magnitude of the vorticity is larger 
so the erosion is getting faster and faster 
from the first snapshot to the forth one in Fig.~\ref{fig:Eroding100vort}.
At t = 0.005 the porosity is 55.54\% and the most gap sizes between bodies are less than 0.015 in 
Fig.~\ref{fig:Eroding100gap}(a). Since some of the bodies are vanished in the fluid, the numner of gaps 
decreases and the gap sizes get larger and larger between the remaining bodies. 
In Fig.~\ref{fig:Eroding100gap}(b) and (c) we still can see small gap sizes are in the majority but 
it is not as concentrated as the one we see in  Fig.~\ref{fig:Eroding100gap}(a). 
\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/gap_hist100_50}
\caption{100 bodies with 318 gaps at t= 0.005}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/gap_hist100_100}
\caption{99 bodies with 312 gaps at t= 0.01}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/gap_hist100_150}
\caption{94 bodies with 294 gaps at t= 0.015}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/gap_hist100_200}
\caption{82 bodies with 254 gaps at t= 0.02}
\end{subfigure}
\caption{\label{fig:Eroding100gap} The histograms of gaps in the case of erosion of 100 bodies at four time steps.}
\end{figure}

To study the behavior of fluid in the porous media with multiple bodies, 
we release 1000 equal spreeding tracers from the 
starting cross section x = -1 and record their trajectories and velocities
until they arrive the end cross section x = 1 
and the porosity of this geometric structure is 62.98 \%. 
To understand the global action of fluid qualitatively, 
we only draw 200 historical trajectories from x = -1 to x = 1 
in Fig.~\ref{fig:Eroding100tracer}.

>>>>

{\color{red}
This case is 100 bodies in a Hagen-Poiseuille flow. The background
flow is 
\begin{align}
  \UU(\xx)=U \left[
  \begin{array}{c}
    1-y^2 \\ 0
  \end{array}
  \right]
\end{align}
with floating flow rate $U$ such that pressure drop is fixed from x = -2 to x = 2.
We record the vorticity of 
fluid in colormap during the bodies erosion in Fig.~\ref{fig:Eroding100vort} and 
measure the gap sizes between bodies in Fig.~\ref{fig:Eroding100gap} at four equispaced times.
Since the vorticity is equivalent to the shear stress and the erosion is faster in the regions where
the magnitude of the vorticity is larger 
so the erosion is getting faster and faster 
from the first snapshot to the forth one in Fig.~\ref{fig:Eroding100vort}.
At t = 0.005 the porosity is 55.54\% and the most gap sizes between bodies are less than 0.015 in 
Fig.~\ref{fig:Eroding100gap}(a). Since some of the bodies are vanished in the fluid, the numner of gaps 
decreases and the gap sizes get larger and larger between the remaining bodies. 
In Fig.~\ref{fig:Eroding100gap}(b) and (c) we still can see small gap sizes are in the majority but 
it is not as concentrated as the one we see in Fig.~\ref{fig:Eroding100gap}(a). 
In Fig.~\ref{fig:Eroding100gap}(d) there are only 254 gaps between 82 bodies and 
the distribution of gap sizes spreads over without any major pack.  
\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/gap_hist100_50}
\caption{100 bodies with 318 gaps at t= 0.005}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/gap_hist100_100}
\caption{99 bodies with 312 gaps at t= 0.01}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/gap_hist100_150}
\caption{94 bodies with 294 gaps at t= 0.015}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/gap_hist100_200}
\caption{82 bodies with 254 gaps at t= 0.02}
\end{subfigure}
\caption{\label{fig:Eroding100gap} The histograms of gaps in the case of erosion of 100 bodies at four time steps.}
\end{figure}

To study the behavior of fluid in the porous media with multiple bodies, 
we release 1000 tracers equispaced in $y$ from the 
cross section x = -1 and record their trajectories and velocities
until they arrive the end cross section x = 1 
and the porosity of this geometric structure is 62.98 \%. 
To understand the global action of fluid qualitatively, 
we only draw 200 historical trajectories from x = -1 to x = 1 
in Fig.~\ref{fig:Eroding100tracer}. 
When equispaced tracers are released in a 2D tube without any grains, 
the streamlines are straight 
and the intersection points of streamlines and any cross section are equispaced. 
But it is not the same when there are bodies in the fluid. 
In Fig.~\ref{fig:Eroding100tracer}
even the tracers are equispaced in $y$ on the cross section $S$, 
the streamlines have been push up and down by the bodies and
some of them are close together.
